Applying Automated Verification to Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-04-25 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated text ASE

To select an optimum combination to meet sizing constraints, we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system is made by the best compromise between those two objectives (power reliability and system cost)~\cite{Alsadi2018}. 
Regarding power reliability, the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean? Remember that we have software engineering audience}.

However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC). Here, one more time, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the maintenance or operational costs \textcolor{red}{cite a reference here}.

@@

The sizing project check of the inverter is carried out by means of three equations. Equation~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Equation~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$). Where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
%
\begin{equation}
\label{eq:vindc} 
\scriptstyle V_{in}DC = \scriptstyle V_{system}.
\end{equation}
%
\begin{equation}
\label{eq:voutac} 
\scriptstyle V_{out}AC = \scriptstyle V_{AC}.
\end{equation}
%
\begin{equation}
\label{eq:invcheck} 
\left[ (\scriptstyle Demand \leq \scriptstyle P_{AC,ref}) \, \scriptstyle and \, \scriptstyle (P_{surge} \leq MAX_{AC,ref}) \right].
\end{equation}

@@

 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE $initialize \, variables$ \\
  \STATE $declare \, list \, of \, PV \, panels \, data \, and \, cost $ \\
  \STATE $declare \, list \, of \, controllers \, data \, and \, cost $ \\
  \STATE $declare \, list \, of \, batteries \, data \,  and \, cost $ \\
  \STATE $declare \, list \, of \, inverters \, data \,  and \, cost $ \\
  \STATE $declare \, the \, maximum \, cost \, possible \, MaxCost $  \\
  \STATE $declare \, power \, demand, \, power \, peak, \, energy \, consumption $ \\
  \STATE $declare \, battery\,  autonomy, deep \, of \, discharge, AC \, voltage$ \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE $declare \, non-det \, variable \, to \, select \, Panel \, from \, list$ \\
 	\STATE $declare \, non-det \, variable \, to \, select \, Controller \, from \, list $ \\
 	\STATE $declare \, non-det \, variable \, to \, select \, Battery \, from \, list $ \\
 	\STATE $declare \, non-det \, variable \, to \, select \, Inverter \, from \, list $ \\ 	
 	\STATE $calculate \, E_{corrected}, \, E_{p} $ \\
	\STATE $calculate \, N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE $calculate \, C_{bank}$ \\
	\STATE $calculate \, N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{c})$ \\
 	\STATE $calculate \, I_{sc,amb}$ \\
 	\STATE $calculate \, I_{c,min}$ \\
 	\STATE $requeriment \, enforced \, by \, \textbf{assume}(I_{c})$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{in}DC)$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{out}AC)$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(Demand)$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(P_{surge})$ \\
	\STATE $non-det \, variables \, hold \, feasible \, equipment \, and \ cost $ \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
	\STATE $Violation \, check \, with \, \textbf{assert}(F_{obj} \geq HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
  \end{scriptsize}
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}

@@

Next, we use the equations described in Section~\ref{sec:sizing} \textcolor{red}{which equations? please be more specific?} to calculate the sizing variables (Lines 14 to 20). The directive \textit{assume} (from Line 21 to 25) ensures the compatibility of the chosen items from the list of equipment: the automatic verification uses only the item (among all the possible ones) that satisfies the statements from Line 14 to 20 in addition to the Line 18. Therefore, our algorithm reaches Line 27 with one feasible solution, and the cost of that solution is calculated in $F_{obj}$.

@@

\textcolor{red}{What are the main challenges for the verification part?}

>>>>

@@

The sizing project check of the inverter is carried out by means of three equations. Equation~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Equation~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$). Where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
%
\begin{equation}
\label{eq:vindc} 
\scriptstyle V_{in}DC = \scriptstyle V_{system}.
\end{equation}
%
\begin{equation}
\label{eq:voutac} 
\scriptstyle V_{out}AC = \scriptstyle V_{AC}.
\end{equation}
%
\begin{equation}
\label{eq:invcheck} 
\left[ (\scriptstyle Demand \leq \scriptstyle P_{AC,ref}) \, \scriptstyle and \, \scriptstyle (P_{surge} \leq MAX_{AC,ref}) \right].
\end{equation}
% -------------------------------------------------------
\section{Optimum sizing of PV systems}
% -------------------------------------------------------
To select an optimum combination of compontntes from a PV system in order to meet sizing constraints, we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system is made by the best compromise between those two objectives (power reliability and system cost)~\cite{Alsadi2018}.

Regarding power reliability, the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean? Remember that we have software engineering audience}.

However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC). Here, one more time, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.

@@

 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE $initialize \, variables$ \\
  \STATE $declare \, list \, of \, PV \, panels \, data \, and \, cost $ \\
  \STATE $declare \, list \, of \, controllers \, data \, and \, cost $ \\
  \STATE $declare \, list \, of \, batteries \, data \,  and \, cost $ \\
  \STATE $declare \, list \, of \, inverters \, data \,  and \, cost $ \\
  \STATE $declare \, the \, maximum \, cost \, possible \, MaxCost $  \\
  \STATE $declare \, power \, demand, \, power \, peak, \, energy \, consumption $ \\
  \STATE $declare \, battery\,  autonomy, deep \, of \, discharge, AC \, voltage$ \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE $declare \, non-det \, variable \, to \, select \, Panel \, from \, list$ \\
 	\STATE $declare \, non-det \, variable \, to \, select \, Controller \, from \, list $ \\
 	\STATE $declare \, non-det \, variable \, to \, select \, Battery \, from \, list $ \\
 	\STATE $declare \, non-det \, variable \, to \, select \, Inverter \, from \, list $ \\ 	
 	\STATE $calculate \, E_{corrected}, \, E_{p} $ \\
	\STATE $calculate \, N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE $calculate \, C_{bank}$ \\
	\STATE $calculate \, N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{c})$ \\
 	\STATE $calculate \, I_{sc,amb}$ \\
 	\STATE $calculate \, I_{c,min}$ \\
 	\STATE $requeriment \, enforced \, by \, \textbf{assume}(I_{c})$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{in}DC)$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{out}AC)$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(Demand)$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(P_{surge})$ \\
	\STATE $non-det \, variables \, hold \, feasible \, equipment \, and \ cost $ \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
	\STATE $Violation \, check \, with \, \textbf{assert}(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
  \end{scriptsize}
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}

@@

Next, we use Eq.~(\ref{eq:Ecorrected}), Eq.~(\ref{eq:Ep}), Eq.~(\ref{eq:NTPmin}), Eq.~(\ref{eq:NPSmin}), Eq.~(\ref{eq:NPPmin}), Eq.~(\ref{eq:Cbank}), Eq.~(\ref{eq:Nbtotal}), Eq.~(\ref{eq:iscamb}), and Eq.~(\ref{eq:icmin}) to calculate the sizing variables (Lines 14 to 20). The directive \textit{assume} (from Line 21 to 25) ensures the compatibility of the chosen items from the list of equipment: the automatic verification uses only the item (among all the possible ones) that satisfies the statements from Line 14 to 20 in addition to the Line 18. Therefore, our algorithm reaches Line 27 with one feasible solution, and the cost of that solution is calculated in $F_{obj}$.

@@

\textcolor{red}{The main challenge for the verification part is to found a feasible solution (technically speaking, regarding the constraints and user requirements) that is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is inputted to the tool}.
